Choose a License

### 2024-11-28 choose_license.qmd
Use appropriate callouts
Fix diagram

---
title: "Choose a License"
lang: en
format:
  html:
    mermaid:
      theme: neutral
engine: knitr
---

@@

::: {#cau-exclusive-rights .callout-caution}
### Giving Publishers Exclusive Rights

@@

  subgraph "License for combination of data (database)"
  choose_license --> switch_license["<em>Depending on content license</em>"]
  use_existing_license_content --> switch_license

>>>>

---
title: "Choose a License"
lang: en
engine: knitr
---

@@

::: {#wrn-exclusive-rights .callout-warning}
### Giving Publishers Exclusive Rights

@@

  subgraph "License for combination of data (database)"
  choose_license --> switch_license["<em>Depending on<br>content license</em>"]
  use_existing_license_content --> switch_license
